2-rules

### 2017-12-05 analysis/analyses/3-score_rules/1-generate-toys.Rmd
reordered analyses
update to toy rules

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Generate toy datasets for comparing scores
```{r}
library(tidyverse)
library(dyneval)

source("generation.R")
source("perturbation.R")
```

```{r}
toys_blueprint <- tribble(
  ~generator_id, ~perturbator_id,
  "linear", "gs",
  "linear", "switch_two_cells",
  "linear", "switch_all_cells",
  "linear", "join_linear",
  "linear", "split_linear",
  "linear", "warp",
  "linear", "hairy",
  "linear", "hairy_small",
  "linear", "hairy_large",
  "linear", "remove_cells",
  "linear", "add_distant_edge",
  "linear", "structure_and_position",
  "bifurcating", "gs",
  "bifurcating", "change_lengths",
  "bifurcating", "change_terminal_lengths",
  "bifurcating", "switch_two_cells",
  "bifurcating", "switch_all_cells",
  "bifurcating", "warp",
  "bifurcating", "hairy",
  "bifurcating", "remove_cells",
  "bifurcating", "add_distant_edge",
  "bifurcating", "structure_and_position",
  "cycle", "gs",
  "cycle", "switch_all_cells",
  "cycle", "break_cycles",
  "cycle", "warp",
  "cycle", "hairy",
  "cycle", "remove_cells",
  "cycle", "add_distant_edge"
) %>% 
  bind_rows(tibble(generator_id="linear", perturbator_id=paste0("switch_", percs * 100))) %>%
  rowwise() %>% 
  mutate(
  generator=list(get(paste0("generate_", generator_id))),
  perturbator=list(get(paste0("perturb_", perturbator_id)))
)

# replicate
nreplicates <- 1
toys <- toys_blueprint %>% slice(rep(1:n(), each=nreplicates)) %>% mutate(
  replicate=seq_len(nrow(.))%%nreplicates,
  toy_category=paste0(generator_id, "-", perturbator_id),
  toy_id=paste0(toy_category, "-", replicate)
) %>%
  mutate(ncells=sample(50:500, n(), replace=TRUE))

# generate gold standards and toys, can take some time (for computing the geodesic distances I presume)
# I choose to not do this using mutate because it is much easier to debug using loops
toys$gs <- toys %>% split(seq_len(nrow(toys))) %>% parallel::mclapply(function(row) {
  row$generator[[1]](row$ncells)
}, mc.cores=8)
#toys$gs <- map2(toys$generator, toys$ncells, ~.x(.y))

@@

write_rds(toys, "toys.rds")
```

```{r}
toys <- read_rds("toys.rds")

@@

metrics <- c("mean_R_nx", "auc_R_nx", "Q_local", "Q_global", "correlation", "isomorphic", "robbie_network_score", "mantel_pval", "ged")

results <- toys %>% rowwise() %>% do(compare_gs_toy(.$gs, .$toy, .$gs_grouped))# %>% select(-starts_with("time"))
scores <- results %>% select(-starts_with("time"))

write_rds(scores, "scores.rds")
```

@@

timings %>% 
  left_join(metric_groups, by="metric_group_id") %>% 
  write_rds("timings.rds")
```

>>>>

```{r setup}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(dynalysis)
library(tidyverse)
library(dyneval)
```

## Generate toy datasets for comparing scores
```{r}
source("analysis/analyses/3-score_rules/generation.R")
source("analysis/analyses/3-score_rules/perturbation.R")

experiment("score_rules")
```

```{r}
toys_blueprint <- tribble(
  ~trajectory_type, ~perturbator_id,
  "simple_linear", "gs",
  "simple_linear", "switch_two_cells",
  "simple_linear", "switch_all_cells",
  "simple_linear", "join_linear",
  "simple_linear", "split_linear",
  "simple_linear", "warp",
  "simple_linear", "hairy",
  "simple_linear", "hairy_small",
  "simple_linear", "hairy_large",
  "simple_linear", "remove_cells",
  "simple_linear", "add_distant_edge",
  "simple_linear", "structure_and_position",
  "bifurcating", "gs",
  "bifurcating", "change_lengths",
  "bifurcating", "change_terminal_lengths",
  "bifurcating", "switch_two_cells",
  "bifurcating", "switch_all_cells",
  "bifurcating", "warp",
  "bifurcating", "hairy",
  "bifurcating", "remove_cells",
  "bifurcating", "add_distant_edge",
  "bifurcating", "structure_and_position",
  "cycle", "gs",
  "cycle", "switch_all_cells",
  "cycle", "break_cycles",
  "cycle", "warp",
  "cycle", "hairy",
  "cycle", "remove_cells",
  "cycle", "add_distant_edge"
) %>% 
  bind_rows(tibble(trajectory_type="simple_linear", perturbator_id=paste0("switch_", percs * 100))) %>%
  bind_rows(crossing(trajectory_type=trajectory_types, perturbator_id=paste0("change_network_", trajectory_types)) %>% mutate(ncells = 5)) %>% 
  rowwise() %>% 
  mutate(
  perturbator=list(get(paste0("perturb_", perturbator_id)))
)

# replicate
nreplicates <- 1
toys <- toys_blueprint %>% slice(rep(1:n(), each=nreplicates)) %>% mutate(
  replicate=seq_len(nrow(.))%%nreplicates,
  toy_category=paste0(trajectory_type, "-", perturbator_id),
  toy_id=paste0(toy_category, "-", replicate)
) %>%
  mutate(ncells=sample(50:500, n(), replace=TRUE))

# generate gold standards and toys, can take some time (for computing the geodesic distances I presume)
# I choose to not do this using mutate because it is much easier to debug using loops
toys$gs <- toys %>% split(seq_len(nrow(toys))) %>% parallel::mclapply(function(row) {
  generate_dataset(row$trajectory_type, row$ncells)
}, mc.cores=8)
#toys$gs <- map2(toys$generator, toys$ncells, ~.x(.y))

@@

write_rds(toys, derived_file("toys.rds"))
```

```{r}
toys <- read_rds(derived_file("toys.rds"))

@@

metrics <- c("mean_R_nx", "auc_R_nx", "Q_local", "Q_global", "correlation", "isomorphic", "node_edit_score", "node_edge_edit_score", "mantel_pval", "ged")

library(PRISM)

qsub_run(
  function(x) {
    library(tidyverse)
    parallel::mclapply(seq_len(nrow(toys)), function(row_id) {
      row <- dynutils::extract_row_to_list(toys, row_id)
      compare_gs_toy(.$gs, .$toy, .$gs_grouped)
    })
  },
  qsub_config = override_qsub_config(num_cores = 24),
  qsub_environment = list2env(list(compare_toy, compare_gs_toy, toys)
)

scores <- results %>% select(-starts_with("time"))

write_rds(scores, result_file("scores.rds"))
```

@@

timings %>% 
  left_join(metric_groups, by="metric_group_id") %>% 
  write_rds(result_file("timings.rds"))
```

### 2017-12-05 analysis/analyses/3-score_rules/2-rules.Rmd
update to toy rules

```{r}
library(tidyverse)
library(dyneval)
```

```{r}
scores <- read_rds("scores.rds")
toys <- read_rds("toys.rds")
timings <- read_rds("timings.rds")

@@

source("rules.R")
rules_info$check_func <- map(paste0("check_", rules_info$id), get)

@@

metric_types <- rep("positional", length(unique(scores_summary$score_id))) %>% setNames(unique(scores_summary$score_id))
metric_types[c("ged", "robbie_network_score", "isomorphic")] <- "structural"

>>>>

```{r setup}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(dynalysis)
library(tidyverse)
library(dyneval)
```

```{r}
experiment("score_rules")

scores <- read_rds(result_file("scores.rds"))
toys <- read_rds(derived_file("toys.rds"))
timings <- read_rds(result_file("timings.rds"))

@@

source("analysis/analyses/3-score_rules/rules.R")
rules_info$check_func <- map(paste0("check_", rules_info$id), get)

@@

metric_types <- rep("positional", length(unique(scores_summary$score_id))) %>% setNames(unique(scores_summary$score_id))
metric_types[c("ged", "robbie_network_score", "lies_network_score", "isomorphic")] <- "structural"
